---
title: "Leaks, Attribution, and Academic Research"
subtitle: "A Case for Professional Reflexivity"
author: 
  - Thomas Fox
thanks: "Code and data are available at: https://github.com/ThomasWilliamFox/leaks_attribution_research.git; Replication on Social Science Reproduction Platform can be found at: https://doi.org/10.48152/ssrp-zvgn-8j27"
date: today
date-format: long
abstract: "Researchers face serious ethical and professional issues when considering millions of classified documents released by WikiLeaks as potential research materials. This paper examines trends in top-rated international relations journals that apparently cite or make reference to these materials in publications between 2010 and 2020. Findings indicate an increase in articles published by peer-reviewed journals that cite these materials, and a lack of professional consistency while doing so. This suggests the need for clear professional consensus within the research community surrounding these ethically questionable materials."
format: pdf
number-sections: true
toc: true
bibliography: references.bib
nocite: |
  @tellingstories
---

```{r}
#| include: false
#| warning: false
#| message: false
#| echo: false

library(tidyverse)
library(knitr)
library(here)
library(dplyr)
library(janitor)
```

```{r}
#| include: false
#| warning: false
#| message: false
#| echo: false

#### Load data ####

# read publication data

journal_data = read_csv(
  file = here("data/analysis_data/publication_analysis_data.csv"),
  show_col_types = FALSE
)

# read cleaned child care data

journal_key = read_csv(
  file = here("data/analysis_data/journal_key_analysis_data.csv"),
  show_col_types = FALSE
)
```

# Introduction

Researchers in various fields are guided by frameworks established by professional bodies and institutions while conducting research and publishing their work. Paleontologists and art historians for instance put considerable emphasis on the provenance of fossils and artworks while considering whether or not to engage with these sources [@darnton]. These procedures aim to ensure that ethical practices are involved in the procurement of these objects and to verify that these sources of information are trustworthy and authentic [@darnton]. As millions of classified government documents are leaked via digital platforms like WikiLeaks, researchers in political science and international relations are given little professional guidance surrounding the temptation to use these sources of information in their research [@darnton].

This paper follows a reproduction of Darnton's 2022 paper, "The Provenance Problem: Research Methods and Ethics in the Age of WikiLeaks" by examining its replication data made available through the Harvard Dataverse [@darntondata]. The analysis of the data was carried out with the programming language `R` [@citeR]. Various packages were used in the processing, cleaning, and presentation of this information, including `tidyverse` [@tidyverse], `knitr` [@knitr], `here` [@here], `dplyr` [@dplyr], and `janitor` [@janitor].

This analysis shows that influential, editorial, non-peer reviewed international relations journals may have set a precedent of publishing articles apparently referencing leaked classified materials in the years following the "Iraq War Logs" leak in 2010 [@darnton]. The paper's estimand is that as the numbers of articles published by these journals declined, peer-reviewed academic journals began publishing articles apparently referencing leaked classified documents with increasing frequency. These articles are inconsistently cited, provide little justification for using such materials, and rarely discuss the implications of these practices. A framework similar to that discussed by @darnton is supported by these findings as a potential means of encouraging professional reflexivity and consistency in academic and professional research.

This remainder of this paper contains an outline of the data examined, an analysis of the data, and a discussion of the findings. [@sec-data] outlines the analysis data made available by Darnton [@darntondata]. [@sec-journals] examines the TRIP-20 journals and their ratings @trip. [@sec-publications] outlines the data-set built by Darnton, consisting of information about articles that apparently use classified materials [@darntondata]. An exploration and analysis of the data is found in [@sec-results]. The paper concludes with a discussion surrounding the paper's findings, including potential weaknesses and further research [@sec-discussion].

# Data {#sec-data}

## TRIP Survey International Relations Journals (2011) {#sec-journals}

The 2011 Teaching, Research, and International Policy (TRIP) faculty survey was published in 2012 as part of the TRIP Project at The Institute for the Theory and Practice of International Relations at the College of William & Mary in Williamsburg, Virginia [@trip]. The survey, collected responses from 3464 political science, international relations, and foreign policy professionals across 20 countries [@trip]. The table on page 52 of the publication is a world-wide aggregate of responses on two questions surrounding which journals have the "greatest influence on the way IR scholars think about international relations" [@trip]. The top 20 journals from the TRIP survey were used the basis for Darnton's analysis data set of articles apparently referencing classified documents [@darnton]. @tbl-publicationnames, is built using data found within Darnton's replication data set [@darntondata]. The data consists of the names of the 20 journals, their short form abbreviations used by Darnton, as well as their ranking in the TRIP survey, with 1 being most influential and 20 being the least.

```{r}
#| label: tbl-publicationnames
#| tbl-cap: Names, Shortform, and TRIP-20 ratings of the 20 Journals
#| warning: false
#| message: false
#| echo: false

# Arrange key by TRIP rating

journals <- 
  arrange(journal_key, trip_rating)

# Build table 

journals|>
  kable(col.names = c("Journal Name", "Short Form", "TRIP-20 Rating"),
    booktabs = TRUE
  ) 
```

## Articles Apparently Referencing Materials From WikiLeaks (2010 - 2020) {#sec-publications}

A data set containing information related to articles apparently referencing classified materials released by WikiLeaks was constructed by Darnton as part of their paper [@darnton]. The terms, "Wikileaks", "cable", and a combination of the two were used to search for articles published between 2010 and 2020 in TRIP rated journals. Darnton used data bases such as JSTOR, Project Muse, and ProQuest, as well as publisher platforms including Sage, Wiley, and Oxford University Press to locate the articles contained in the data set [@darnton]. Of the 565 articles produced through their search, 397 were false positives (mentioned WikiLeaks organization or physical cables). Darnton read and itemized each of the 168 remaining articles to build their analysis data set [@darnton].

@tbl-publicationdata is built using Darnton's replication data [@darntondata]. The data set contains 168 entries, each corresponding to an article in a TRIP rated journal that apparently references classified documents released by WikiLeaks. The "code" variable refers to Darnton's coding system, with "2" representing articles that refer to these materials via secondary sources, and "3" representing articles that quote, cite, or paraphrase materials from WikiLeaks directly [@darnton]. The "Journal" and "Year" variables refer to the journal that published the article and the year in which it was published.

```{r}
#| label: tbl-publicationdata
#| tbl-cap: Sample of Cleaned Academic Publication Data
#| warning: false
#| message: false
#| echo: false

# Build first half of publication data table

head(journal_data[c(1:6)], 6) |>
  kable(col.names = c("Code",
                      "Journal", "Year", "Mentions 'Classified'",
                      "No Source", "Mentions 'Leak'"),
        align = 'l',
    booktabs = TRUE
  ) 
```

```{r}
#| label: tbl-publicationdata2
#| warning: false
#| message: false
#| echo: false

# Builds second half of publication data table

head(journal_data[c(7:12)], 6) |>
  kable(col.names = c("Uses euphemism", "WikiLeaks' cable", "To-From-Found", "Peer Reviewed", 
                      "Cable Discussed", "Cable(s) Cited"),
        align = 'l',
    booktabs = TRUE,
  ) 
```

Various variables coded as "y" for yes and "n" for no are used in Darnton's data set. The "Classified" variable indicates whether the article makes reference to the classified nature of the materials [@darnton]. "No Source" indicates that at least one referenced document is missing a citation. "Leak" indicates that the article mentions leaked nature of sources. "Uses Euphemism" refers to articles that use verbs other than leak such as "publish, or disseminate." "WikiLeaks' cable" indicates if an article refers to a document or cable as the possession of WikiLeaks rather than its true source. The "To-From-Found" variable describes whether citations include an "author (can be "embassy"), recipient (even "State"), and repository" [@darnton]. "Peer reviewed" indicates whether the journal is peer reviewed. "Cable Discussed" indicates whether an article discusses leaked US cables and the "Cables Cited" variable communicates how many individual leaked cables are cited.

@fig-totalarticles displays all 168 articles published in TRIP rated journals from 2010-2020 that apparently cite or reference leaked documents from WikiLeaks directly or through secondary sources. The years with the greatest number of articles published are 2011 with 24, 2013 with 21, and 2016 with 20. The Journals that published the most articles according to the data set are International Affairs (IA) with 29, Foreign Policy (FP) with 25, and International Security (IS) with 16.

```{r}
#| label: fig-totalarticles
#| fig-cap: Articles in TRIP rated Journals apparently citing leaked classified material either directly or indirectly between 2010 and 2020
#| warning: false
#| message: false
#| echo: false

# Builds graph with each published article citing leaked classified documents
# Each bar is filled with the proportion of articles published by each journal per year 

filter(journal_data) |>
  ggplot(aes(x = as.character(`year`), fill = journal)) +
  geom_bar() +
  theme_minimal() +
  scale_fill_grey() +
  labs(x = "Year", y = "Articles", fill = "Journal") +
  theme(legend.position = "bottom")
```

# Results {#sec-results}

To better understand the publication trends in these articles, this section will explore an analysis of the articles directly citing apparently classified documents. We will focus on differences in trends between peer-reviewed and non-peer-reviewed journals as well as citation attributes in the articles published by academic journals using these materials. 

@fig-peerarticles displays articles that apparently directly cite leaked classified materials in peer-reviewed journals. 81 articles in peer-reviewed TRIP rated journals apparently used such materials. The Journals with the greatest number of articles citing apparently leaked materials are International Affairs (IA) with 14, International Security (IS) with 10, as well as the Review of International Studies (RIS) and Security Studies (SS) with 9 each. This graph indicates an upward trend in publications in these journals from 2010 to 2020 with the greatest number of articles published in 2016, 2018, and 2019.  

```{r}
#| label: fig-peerarticles
#| fig-cap:  Articles in peer-reviewed TRIP rated Journals apparently citing leaked classified material directly between 2010 and 2020
#| warning: false
#| message: false
#| echo: false
#| fig.pos: "H"

journal_peer <-
  filter(journal_data, code == 3, peer == 'y') 

journal_peer |>
  ggplot(aes(x = as.character(`year`), fill = journal)) +
  geom_bar() +
  theme_minimal() +
  scale_fill_grey() +
  labs(x = "Year", y = "Articles", fill = "Journal") +
  theme(legend.position = "bottom")

```

@fig-fafparticles shows the articles apparently directly citing classified materials published by Foreign Affairs magazine and Foreign Policy magazine, both non-academic, editorial journals [@darnton]. Foreign Affairs (FA) published 10 articles referencing such materials and Foreign Policy (FP) published 25. The majority of these articles were published from 2011 to 2013 where Foreign Policy published 22 articles and Foreign Affairs published 6, after which a sharp decline in articles released by these publications can be seen. 

```{r}
#| label: fig-fafparticles
#| fig-cap: Articles in Foreign Affairs and Foreign Policy Magazines apparently citing leaked classified material directly between 2010 and 2020
#| warning: false
#| message: false
#| echo: false
#| fig.pos: "H"

journal_peer <-
  filter(journal_data, code == 3, peer == 'n') 

journal_peer |>
  ggplot(aes(x = as.character(`year`), fill = journal)) +
  geom_bar() +
  theme_minimal() +
  scale_fill_grey() +
  labs(x = "Year", y = "Articles", fill = "Journal") +
  theme(legend.position = "bottom")

```

@fig-peerpoorprac shows the number of peer reviewed articles that either fail to mention the classified nature of the materials cited, omit any reference to the materials being leaked, or fail to properly cite the cable being referenced according to the to-from-found format outlined in @sec-publications. Any one of these attributes suggests that an article fails to communicate the true source of the utilized information. Of the articles in this group, 12 were published by International Affairs (IA), 8 by International Security, and 7 each by International Studies (RIS) and Security Studies (SS). Of the 64 articles that had one of the attributes outlined above, 33 articles had all three. 

```{r}
#| label: fig-peerpoorprac
#| fig-cap: Articles in peer-reviewed TRIP rated Journals directely referencing apparently classified materials but failing to either communicate their apparently classified nature, mention their leaked orgin, or use a to-from-found citation format. 
#| warning: false
#| message: false
#| echo: false
#| fig.pos: "H"

journal_peer <-
  filter(journal_data, code == 3, peer == 'y', cable == 'y', classified == 'n' | leak == 'n'| to_from_found == 'n') 

journal_peer |>
  ggplot(aes(x = as.character(`year`), fill = journal)) +
  geom_bar() +
  theme_minimal() +
  scale_fill_grey() +
  labs(x = "Year", y = "Articles", fill = "Journal") +
  theme(legend.position = "bottom")

```

@fig-peergoodprac demonstrates peer-reviewed journal articles articles that either discuss the classified nature of the material, discuss the fact that the materials were leaked, or contain a "to-from-found" citation (see @sec-publications). Journals with the greatest number of articles that display one of these attributes are International Affairs (IA) with 7, International Security (IS) with 5, and 4 each by International Studies (RIS) and Security Studies (SS). It is worth noting that none of the 31 articles in this group display all three attributes.

```{r}
#| label: fig-peergoodprac
#| fig-cap: Articles in peer-reviewed TRIP rated Journals directly referencing apparently classified materials and either properly communicating their apparently classified nature, mentioning their leaked orgin, or using a to-from-found citation format. 
#| warning: false
#| message: false
#| echo: false
#| fig.pos: "H"

journal_peer <-
  filter(journal_data, code == 3, peer == 'y', classified == 'y' | leak =='y' | to_from_found == 'y') 


journal_peer |>
  ggplot(aes(x = as.character(`year`), fill = journal)) +
  geom_bar() +
  theme_minimal() +
  scale_fill_grey() +
  labs(x = "Year", y = "Articles", fill = "Journal") +
  theme(legend.position = "bottom")

```

These findings point to an increase in articles being published that apparently utilize these materials by peer-reviewed academic international relations journals. Although Foreign Affairs and Foreign Policy Magazine are not academic journals, they are both in the top ten most influential journals in the field of international relations (4 and 9 respectively) as outlined in the 2011 TRIP survey [@trip]. The lack of consistency in disclosure regarding the nature of these documents in many of these articles obscures their source as well as the ethical implications surrounding their use. Many articles attempt to clearly communicate the source of these materials, but as Darnton points out, very few discuss the reasons for relying on them [@darnton].

# Discussion {#sec-discussion}

## Upward Trend in Publications {#sec-first-point}
The decreasing number of articles from 2011 to 2020 may suggest that these journals quickly published articles utilizing these sources when they were contextually relevant and moved on to other topics. In doing so, these types of journals may have set a precedent in the international relations publishing community that was followed by TRIP rated peer-reviewed academic journals. 

## A Case for Reflexive Frameworks

## Weaknesses and Next Steps

As this paper has followed a reproduction of Darnton's 2022 paper "The Provenance Problem: Research Methods and Ethics in the Age of WikiLeaks", its provided replication data set has been the basis for the analysis portions of this paper. This data set, as outlined in @sec-publications, was built by Darnton by manually searching various databases for articles containing keywords. After this step Darnton manually recorded all relevant attributes by searching and reading each article that directly cited the apparently classified materials. To conduct a more thorough replication, rebuilding Darnton's data set may be required in order to verify all articles and attributes, although this would require considerable time and resources. Broadening the scope of study may also be beneficial in comparing publication trends to Journals in other disciplines. 

\newpage

\newpage

# References
