---
title: "Leaks, Attribution, and Academic Research"
subtitle: "The Role of Precedence and Normalization in Publication Trends"
author: 
  - Thomas Fox
thanks: "Code and data are available at: https://github.com/ThomasWilliamFox/leaks_attribution_research.git;Replication on Social Science Reproduction Platform can be found at:  https://www.socialsciencereproduction.org/reproductions/302459e5-ae78-49cf-82d1-265bfe0ad5f1/index"
date: today
date-format: long
abstract: "Serious ethical and professional issues face the researcher community while considering the millions of classified documents released by WikiLeaks as potential research tools. This paper examines publication trends in top-rated international relations journals that cite or make reference to classified documents released by Wikileaks. This paper finds both a lack of professional consistency and an increase in the use of these documents in publications by peer-reviewed journals between 2010 and 2020. This finding suggests the need for clear professional consensus within the research community surrounding these ethically questionable materials."
format: pdf
number-sections: true
toc: true
bibliography: references.bib
nocite: |
  @tellingstories
---

```{r}
#| include: false
#| warning: false
#| message: false
#| echo: false

library(tidyverse)
library(knitr)
library(here)
```

```{r}
#| include: false
#| warning: false
#| message: false
#| echo: false

#### Load data ####

# read publication data
journal_data = read_csv(
  file = here("data/analysis_data/publication_analysis_data.csv"),
  show_col_types = FALSE
)

# read cleaned child care data
journal_key = read_csv(
  file = here("data/analysis_data/journal_key_analysis_data.csv"),
  show_col_types = FALSE
)
```


# Introduction

First Paragraph. (Why it matters)

Second Paragraph. (What it does)

Third Paragraph. (What is found)

Fourth Paragraph. (Paper layout)

You can and should Cross-reference sections and sub-sections. We use @citeR as well as packages such as @tidyverse, @knitr, @here, @dplyr, @janitor. We replicate @darnton using @darntondata and @trip. 

The remainder of this paper is structured as follows. @sec-data....


# Data {#sec-data}

## TRIP-20 Political Science and Foreign Policy Publications {#sec-journals}

Some of our data is about journals (@tbl-publicationnames).

```{r}
#| label: tbl-publicationnames
#| tbl-cap: Names, Shortform, and TRIP-20 ratings of the 20 journals
#| warning: false
#| message: false
#| echo: false

journals <- 
  arrange(journal_key, trip_rating)

journals|>
  kable(col.names = c("Journal Name", "Short Form", "TRIP-20 Rating"),
    booktabs = TRUE
  ) 
```

## Articles Citing WikiLeaks Documents (2010-2020)  {#sec-publications}

Some of our data is about publication data (@tbl-publicationdata).

```{r}
#| label: tbl-publicationdata
#| tbl-cap: Sample of Cleaned Academic Publication Data
#| warning: false
#| message: false
#| echo: false

head(journal_data[c(1:8)], 6) |>
  kable(col.names = c("Code",
                      "Journal", "Year", "Mentions 'Classified'",
                      "No Source", "No U.S.G.",
                      "Mentions 'Leak'", "Uses euphamism"),
    booktabs = TRUE
  ) 
```

```{r}
#| label: tbl-publicationdata2
#| warning: false
#| message: false
#| echo: false

head(journal_data[c(9:14)], 6) |>
  kable(col.names = c("'Wikileaks' cable'", "To-From-Found"
                      , "Peer Reviewed", "Leak in Body", 
                      "Cable Discussed", "Cable(s) Cited"),
        
    booktabs = TRUE,
  ) 
```

Some of our data is about articles (@fig-totalarticles).

```{r}
#| label: fig-totalarticles
#| fig-cap: Articles in TRIP-20 rated journals apparently citing documents from WikiLeaks by year
#| warning: false
#| message: false
#| echo: false

filter(journal_data, code == 3) |>
  ggplot(aes(x = as.character(`year`), fill = journal)) +
  geom_bar() +
  theme_minimal() +
  scale_fill_viridis_d()+
  labs(x = "Year", y = "Articles") +
  theme(legend.position = "bottom")
```

Some of our data is about articles (@fig-peerarticles).


```{r}
#| label: fig-peerarticles
#| fig-cap: Articles in TRIP-20 rated journals apparently citing documents from WikiLeaks by year
#| warning: false
#| message: false
#| echo: false

journal_peer <-
  filter(journal_data, code == 3, peer == 'y') 

journal_peer |>
  ggplot(aes(x = as.character(`year`), fill = journal)) +
  geom_bar() +
  theme_minimal() +
  scale_fill_viridis_d() +
  labs(x = "Year", y = "Articles") +
  theme(legend.position = "bottom")

```

Some of our data is about articles (@fig-fafpalarticles).


```{r}
#| label: fig-fafparticles
#| fig-cap: Articles in FA and FP apparently citing documents from WikiLeaks by year
#| warning: false
#| message: false
#| echo: false

journal_peer <-
  filter(journal_data, code == '3', peer == 'n') 

journal_peer |>
  ggplot(aes(x = as.character(`year`), fill = journal)) +
  geom_bar() +
  theme_minimal() +
  scale_fill_viridis_d() +
  labs(x = "Year", y = "Articles") +
  theme(legend.position = "bottom")

```

Talk more about it.

And also planes. (You can change the height and width, but don't worry about doing that until you have finished every other aspect of the paper - Quarto will try to make it look nice and the defaults usually work well once you have enough text.)


# Results

Our results are summarized in...

# Discussion

## First discussion point {#sec-first-point}

If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this. 

## Second discussion point

## Third discussion point

## Weaknesses and next steps

Weaknesses and next steps should also be included.

\newpage

\appendix

# Appendix {-}


\newpage


# References


