---
title: "Leaks, Attribution, and Academic Research"
subtitle: "My subtitle if needed"
author: 
  - Thomas Fox
thanks: "Code and data are available at: https://github.com/ThomasWilliamFox/leaks_attribution_research.git;Replication on Social Science Reproduction Platform can be found at:  https://www.socialsciencereproduction.org/reproductions/302459e5-ae78-49cf-82d1-265bfe0ad5f1/index"
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
toc: true
bibliography: references.bib
---

```{r}
#| include: false
#| warning: false
#| message: false
#| echo: false

library(tidyverse)
library(knitr)
library(palmerpenguins)
library(here)
```

Total mentions vs Total citations

Mentions per year 

Mentions vs high profile cases (assange, manning) 

Mentions vs president/gov


```{r}
#| include: false
#| warning: false
#| message: false
#| echo: false

# read publication data
journal_data = read_csv(
  file = here("data/analysis_data/publication_analysis_data.csv"),
  show_col_types = FALSE
)

# read cleaned child care data
journal_key = read_csv(
  file = here("data/analysis_data/journal_key_analysis_data.csv"),
  show_col_types = FALSE
)
```


# Introduction

You can and should Cross-reference sections and sub-sections. We use @citeR and @rohan.

The remainder of this paper is structured as follows. @sec-data....



# Data {#sec-data}

Some of our data is of penguins (@fig-bills), from @palmerpenguins.


```{r}
#| label: tbl-publicationnames
#| tbl-cap: Names, Shortform, and TRIP-20 ratings of the 20 journals
#| warning: false
#| message: false
#| echo: false

journals <- 
  arrange(journal_key, trip_rating)

journals |>
  kable(col.names = c("Journal Name", "Short Form", "TRIP-20 Rating"),
    booktabs = TRUE
  ) 
```



```{r}
#| label: tbl-publicationdata
#| tbl-cap: Sample of Cleaned Academic Publication Data
#| warning: false
#| message: false
#| echo: false

head(journal_data[c(1:8)], 6) |>
  kable(col.names = c("Code",
                      "Journal", "Year", "Classified",
                      "No Source", "No U.S.G.",
                      "Mentions 'leak'", "Uses euphamism"),
    booktabs = TRUE
  ) 
```

```{r}
#| label: tbl-publicationdata2
#| warning: false
#| message: false
#| echo: false

head(journal_data[c(9:14)], 6) |>
  kable(col.names = c("'Wikileaks cable'", "To - From - Found"
                      , "Peer Reviewed", "Body Text Leak", 
                      "Cables", "Number of Cables"),
        
    booktabs = TRUE,
  ) 
```


```{r}
#| label: fig-totalarticles
#| fig-cap: Articles in TRIP-20 rated journals apparently citing documents from WikiLeaks by year
#| warning: false
#| message: false
#| echo: false

filter(journal_data, code == 3) |>
  ggplot(aes(x = as.character(`year`), fill = journal)) +
  geom_bar() +
  theme_minimal() +
  scale_fill_viridis_d()+
  labs(x = "Year", y = "Articles") +
  theme(legend.position = "bottom")
```

```{r}
#| label: fig-peerarticles
#| fig-cap: Articles in TRIP-20 rated journals apparently citing documents from WikiLeaks by year
#| warning: false
#| message: false
#| echo: false

journal_peer <-
  filter(journal_data, code == 3, peer == 'y') 

journal_peer
journal_peer |>
  ggplot(aes(x = as.character(`year`), fill = journal)) +
  geom_bar() +
  theme_minimal() +
  scale_fill_viridis_d() +
  labs(x = "Year", y = "Articles") +
  theme(legend.position = "bottom")

```



Talk more about it.

And also planes (@fig-planes). (You can change the height and width, but don't worry about doing that until you have finished every other aspect of the paper - Quarto will try to make it look nice and the defaults usually work well once you have enough text.)


# Results

Our results are summarized in @tbl-modelresults.

# Discussion

## First discussion point {#sec-first-point}

If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this. 

## Second discussion point

## Third discussion point

## Weaknesses and next steps

Weaknesses and next steps should also be included.

\newpage

\appendix

# Appendix {-}


\newpage


# References


